Outdated and License-Violating Code on Stack Overflow

### 2017-10-10 cloverflow-tse/cloverflow.tex
Finished RQ 3.

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	\resizebox{\linewidth}{!}{
		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
			\toprule
			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
			\midrule
			Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
			\midrule
			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
			\bottomrule 
			\multicolumn{10}{l}{{\footnotesize * \textit{S}:
					modified/added/deleted statements, \textit{D}: file
					has been deleted,  \textit{R}: method has been
					rewritten completely}}
		\end{tabular} %
	}
\end{table*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{mod_types}
	\caption{Six code modification found in the latest versions of the outdated clone pairs}
	\label{fig:mod_types}
\end{figure}

We analysed code modifications which made Stack Overflow code outdated by going
though commits and git blame information. The summary of six code modification
types found in the 101 outdated online clone pairs are displayed in
\Cref{fig:mod_types} including statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often
code changes found is statement modification (49 occurrences), followed by statement
addition (29 occurrences), statement removal (18 occurrences), changing of method
signature, i.e.~API change (16 occurrences), and method rewriting (15 occurrences).
Moreover, in the 101 outdated pairs, we found 15 ``dead'' snippets. These snippets
cannot be located in the latest version of the projects. For example,
the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
\textsf{spring}, was deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
Beams on January 20, 2012, two years after it was
posted.

% The latest version of Spring does not contain the file anymore.
\Cref{tab:stale_code_details} shows examples of the outdated online
clones on Stack Overflow. The table displays information of the clones
from both Stack Overflow and Qualitas side including the dates. We
summarise the changes that make the clones outdated into three types,
modified/added/deleted statements (\textit{S}), file deletion
(\textit{D}), and method rewriting (\textit{R}), along with the date
of change. The complete set of 64 outdated online clones can be found
from the study website.

The outdated online code clones cause problems ranging from
uncompilable code (due to modifications and different API usage in the
outdated code) to introducing vulnerabilities to
software~\cite{Xia2014}. An outdated code with a subtle change
(e.g.~\Cref{fig:before-after}) may be copied and reused without
awareness from developers. Although Stack Overflow has a voting
mechanism that may mitigate this issue, the accepted answer is still
used by naive developers who copy and reuse the outdated code.

\textbf{For RQ3, our results show that 57\% (64) of QS clone
	pairs on Stack Overflow are outdated. 60 pairs differ from their
	newest versions by modifications applied to variable names or method
	names, added or deleted statements, to a fully rewritten code with
	new method signatures. 4~pairs are dead
	snippets.}

>>>>

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	\resizebox{\linewidth}{!}{
		\begin{tabular}{cc|lcp{4cm}@{}rrc|lc@{}c}
			\toprule
			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{3}{c}{Changes} \\ 
			\midrule
			Post & Date & Project & Ver. & File & Start & End & Date & Issue ID & Type$^*$ & Date \\
			\midrule
			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & & Bug 439874 & \textit{S} & 17-Mar-15 \\
			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & & LUCENE-4095 & \textit{D} & 31-May-12 \\
			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\
			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 49 & 60 & 7-Dec-09 & 57593 & \textit{R} & 30-Apr-15 \\
			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & N/A & \textit{D} & 20-May-11 \\
			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotation\newline HandlerMapping.java & 78 & 92 & 20-Oct-10 & SPR-14129 & \textit{D} & 20-Jan-12 \\
			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & & WW-4225 & \textit{S} & 18-Oct-13 \\
			\bottomrule 
			\multicolumn{10}{l}{{\footnotesize * \textit{S}:
					modified/added/deleted statements, \textit{D}: file
					has been deleted,  \textit{R}: method has been
					rewritten completely}}
		\end{tabular} %
	}
\end{table*}

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=0.7\linewidth]{mod_types}
%	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
%	\label{fig:mod_types}
%\end{figure}

\begin{table}
	\centering
	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
	\label{tab:mod_types}
		\begin{tabular}{lr}
			\toprule
			Modification & Occurrences \\
			\midrule
			Statement modification & 49 \\
			Statement addition & 29 \\
			Statement removal & 18 \\
			Method signature change & 16 \\
			Method rewriting & 15 \\
			File deletion & 15 \\
			\bottomrule 
		\end{tabular}
\end{table}

We analysed code modifications which made Stack Overflow code outdated by going
though commits and git blame information. The summary of six code modification
types found in the 101 outdated online clone pairs are displayed in
\Cref{tab:mod_types} including statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often code
changes found is statement modification (49 occurrences), followed by statement
addition (29 occurrences), statement removal (18 occurrences), changing of
method signature, i.e.~API change (16 occurrences), and method rewriting (15
occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
snippets. These snippets cannot be located in the latest version of the
projects. For example, the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
January 20, 2012, two years after it was posted.

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that the change is important
and not only a superficial fix such as code formatting.

\Cref{tab:stale_code_details} shows examples of the outdated online clones on
Stack Overflow. The table displays information of the clones from both Stack
Overflow and Qualitas side including the dates. We summarise the changes that
make the clones outdated into three types, modified/added/deleted statements
(\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}),
along with the issue tracking number and the date of change. The complete set of
101 outdated online clones can be found from the study website.

The outdated online code clones cause problems ranging from uncompilable code
(due to modifications and different API usage in the outdated code) to
introducing vulnerabilities to software~\cite{Xia2014}. An outdated code with a
subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
awareness from developers. Moreover, an outdated code with a defect
(e.g.~a race condition problem in \Cref{fig:before-after_2}) is harmful to be reused. Although Stack
Overflow has a voting mechanism that may mitigate this issue, the accepted
answer is still used by naive developers who copy and reuse the outdated code.

\textbf{For RQ3, our results show that 66\% (101) of QS clone pairs on Stack
	Overflow are outdated. 127 pairs differ from their newest versions by
	modifications applied to variable names or method names, added or deleted
	statements, to a fully rewritten code with new method signatures. 15~pairs are
	dead snippets.}
